Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-10-14 Manuscript/manuscript.tex
Improvments in the end of intro

Spectroscopic experiments give detailed information about the
interactions between ions and PS lipids, but the data is often indirect and difficult to
interpret \cite{hauser77,kurland79,eisenberg79,hauser83,dluhy83,hauser85,feigenson86,mattai89,roux90,roux91,boettcher11}.
Classical molecular dynamics (MD) simulations give
access to all the details, but the current force fields are not
sufficiently accurate to interpret the interactions between anionic
lipid headgroups and other lipids or ions \cite{NMRlipidsIV}.
Implicit inclusion of electronic polarizability using
electronic continuum correction (ECC) to lipid models
substantially improved the interactions between cations and
zwitterionic lipids \cite{melcr18}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% On the simulation part .. %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

An empirical scaling factor, which reduces electrostatic forces between molecules, 
is a well known concept in molecular modelling;
such an approach was adopted in the early simulations of lipid bilayers \cite{egberts94, berendsen1996},
in force fields employing explicit polarization \cite{lemkul2016empirical},
or in the simulations of ionic liquids \cite{Bhargava2007}. 
%An improvement of permeability of charged solutes in the gramicidin A channel 
%is observed with a force field using charge equilibration to model polarizability. \cite{lucas2012}

From the perspective of phospholipid bilayers,
a force field with an explicit polarizability 
using the Classical Durde model 
is gradually being developed, however, 
only parameters for PC and PE are available at this moment. \cite{chowdhary13, chowdhary17}
While such a model shows a potential improvement from many perspectives -- 
for example accounting for polarizability has a significant impact on the dipole potential of a membrane \cite{harder2009} -- 
the non-polarizable version of the same force field 
performes comparably well at a fraction of the computational cost 
of the models with explicit polarization. \citep{lucas12,chowdhary13}

%To our knowledge, there is no study focusing on
%charged lipids using polarizable force fields. 
%nor about their interactions with cations and anions. 
%From this perspective,
%this work is the first pioneering study providing atomistic resolution insight 
%into the interactions of POPS with monovalent and even divalent cations.

%Even though the software packages are more and more optimized for running simulations with explicit polarization,
%its application still seems to be rather far from ready for common production use. \cite{jiang2011, lopes2009}

Here, we extend the approach
to anionic PS lipids to more accurately describe their interactions with ions
and PC headgroups in mixed lipid bilayers. The results pave
the way for more realistic MD simulations of negatively charged
lipid bilayers to be used in wide range of applications.

>>>>

Spectroscopic experiments give detailed information about the
interactions between ions and PS lipids, but the data is often indirect and difficult to
interpret \cite{hauser77,kurland79,eisenberg79,hauser83,dluhy83,hauser85,feigenson86,mattai89,roux90,roux91,boettcher11}.
Classical molecular dynamics (MD) simulations give
access to all the details, but the current non-polarizable force fields are not
sufficiently accurate to interpret the interactions between anionic
lipid headgroups and other lipids or ions \cite{NMRlipidsIV}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% On the simulation part .. %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%From the perspective of phospholipid bilayers,
There are force field parameters for neutral lipids PC and PE 
with explicit polarizability using the Classical Durde model. \cite{chowdhary13, chowdhary17}
While such a model shows a potential improvement over non-polarizable force fields from many perspectives -- 
for example accounting for polarizability has a significant impact on the dipole potential of a membrane \cite{harder2009} -- 
the non-polarizable version of the same force field 
performes comparably well at a fraction of the computational cost 
of the models with explicit polarization. \citep{lucas12,chowdhary13}

An empirical scaling factor, which reduces electrostatic forces between molecules, 
is a well known concept in molecular modelling;
such an approach was adopted in the early simulations of lipid bilayers \cite{egberts94, berendsen1996},
in force fields employing explicit polarization \cite{lemkul2016empirical},
or in the simulations of ionic liquids \cite{Bhargava2007}. 
%An improvement of permeability of charged solutes in the gramicidin A channel 
%is observed with a force field using charge equilibration to model polarizability. \cite{lucas2012} 
At the same time, 
the implicit inclusion of electronic polarizability to lipid models
via charge re-scaling using electronic continuum correction (ECC) 
substantially improved the interactions between cations and zwitterionic lipids \cite{melcr18}.

Here, we extend the approach to anionic PS lipids.
The newly developed model termed ECC-POPS 
not only describes the interactions of PS with ions more accurately, 
but also improves the structure of the PS head group 
and its interactions with PC in mixed lipid bilayers. 
The results pave the way to more realistic MD simulations 
of both neutral and negatively charged lipid bilayers 
for a wide range of applications.
